## Data abstraction

Create data sets from studies we had to abstract data from ourselves.
I.e., data did not come from primary source authors or secondary source systematic reviews.

Structure of the data should be

* `author`
* `monthsPostTx`
* `treatmentGroup`
* `cognitiveDomainOriginal` (remove this column since we won't use it)
* `cognitiveDomain`
* `cognitiveTest`
* `scoreType`
* `n`
* `mean`
* `sd`


### Fan

Reference: [Fan 2005, *et al*](http://www.ncbi.nlm.nih.gov/pubmed/16258100).
*J Clin Oncol.* 2005 Nov 1;23(31):8025-32.

Data is in the [Table 9](http://jco.ascopubs.org/content/23/31/8025/T9.expansion.html).

There is a footnote to Table 9:

> NOTE. Higher scores represent better function.

This is different from Trails A and B scores from other studies.
Make sure to account for this different in `combineData.Rmd`.

Fan reports *medians*.
We'll assign their median values to the `mean` variable to keep things consistent.

**Need to figure out what to do with `sd`**

```{r, results='asis'}
D <- rbind(data.table(monthsPostTx= 0, cognitiveTest="Trails A", mean=42.0, sd=NA, n=104, cognitiveDomain="Attn/Wkg Mem/Concentration"),
           data.table(monthsPostTx= 0, cognitiveTest="Trails B", mean=47.5, sd=NA, n=104, cognitiveDomain="Exec Fxn"),
           data.table(monthsPostTx=12, cognitiveTest="Trails A", mean=44.0, sd=NA, n= 91, cognitiveDomain="Attn/Wkg Mem/Concentration"),
           data.table(monthsPostTx=12, cognitiveTest="Trails B", mean=49.0, sd=NA, n= 91, cognitiveDomain="Exec Fxn"),
           data.table(monthsPostTx=24, cognitiveTest="Trails A", mean=47.0, sd=NA, n= 81, cognitiveDomain="Attn/Wkg Mem/Concentration"),
           data.table(monthsPostTx=24, cognitiveTest="Trails B", mean=50.0, sd=NA, n= 81, cognitiveDomain="Exec Fxn"))
D <- D[,
       `:=` (author = "Fan",
             treatmentGroup = "Chemotherapy",
             scoreType = "T score")]
D4a <- D
print(xtable(D4a), type="html")
```


### McDonald

Reference: [McDonald 2012, *et al*](http://www.ncbi.nlm.nih.gov/pubmed/22665542).
*J Clin Oncol.* 2012 Jul 10;30(20):2500-8. doi: 10.1200/JCO.2011.38.5674. Epub 2012 Jun 4

Data is in the [Table A2](http://jco.ascopubs.org/content/30/20/2500/T4.expansion.html) of the appendix.

```{r, results='asis'}
D <- rbind(data.table(monthsPostTx= 0, cognitiveTest="0-back", mean=96.1, sd= 8.2),
           data.table(monthsPostTx= 0, cognitiveTest="1-back", mean=78.3, sd=30.1),
           data.table(monthsPostTx= 0, cognitiveTest="2-back", mean=80.1, sd=27.5),
           data.table(monthsPostTx= 0, cognitiveTest="3-back", mean=66.7, sd=25.2),
           data.table(monthsPostTx=12, cognitiveTest="0-back", mean=88.0, sd=21.9),
           data.table(monthsPostTx=12, cognitiveTest="1-back", mean=89.1, sd=13.2),
           data.table(monthsPostTx=12, cognitiveTest="2-back", mean=83.1, sd=16.1),
           data.table(monthsPostTx=12, cognitiveTest="3-back", mean=68.4, sd=22.9))
D <- D[,
       `:=` (author = "McDonald",
             treatmentGroup = "CTx+",
             cognitiveDomain = "Attn/Wkg Mem/Concentration",
             scoreType = "% accuracy",
             n = 16)]
D4b <- D
print(xtable(D4b), type="html")
```


### Wefel 2010

Reference: [Wefel 2010, *et al*](http://www.ncbi.nlm.nih.gov/pubmed/20564075)
Cancer. 2010 Jul 15;116(14):3348-56. doi: 10.1002/cncr.25098.

Data is in the [Table 4](http://onlinelibrary.wiley.com/doi/10.1002/cncr.25098/full#sec1-2).
Use data from *Time Point 1* and *Time Point 4*.

> Cognitive testing was conducted at baseline [*Time Point 1*] and then on
> average 2.9 months (standard deviation "SD" = 0.59), 7.0 months (SD, 1.4),
> and **13.1 months** (SD = 2.8) after baseline [*Time Point 4*].

```{r, results='asis'}
D <- rbind(data.table(monthsPostTx= 0  , n=42, mean= 0.09, sd=0.86, cognitiveTest="Hopkins Verbal Learning Test Total", cognitiveDomain="Verbal Memory", scoreType="Z-score"),
           data.table(monthsPostTx= 0  , n=42, mean=-0.18, sd=2.51, cognitiveTest="Trail Making Part B", cognitiveDomain="Exec Fxn", scoreType="Z-score"),
           data.table(monthsPostTx= 0  , n=42, mean= 0.29, sd=0.96, cognitiveTest="MAE Controlled Oral Word Association", cognitiveDomain="Verbal Ability/Language", scoreType="Z-score"),
           data.table(monthsPostTx= 0  , n=42, mean=-0.34, sd=1.57, cognitiveTest="Trail Making Part A", cognitiveDomain="Attn/Wkg Mem/Concentration", scoreType="Z-score"),
           data.table(monthsPostTx= 0  , n=42, mean=11.71, sd=2.45, cognitiveTest="WAIS-R Digit Symbol", cognitiveDomain="Information Proc Speed", scoreType="Scaled score"),
           data.table(monthsPostTx= 0  , n=42, mean= 9.00, sd=2.48, cognitiveTest="WAIS-R Digit Span", cognitiveDomain="Attn/Wkg Mem/Concentration", scoreType="Scaled score"),
           data.table(monthsPostTx=13.1, n=28, mean=-0.44, sd=1.23, cognitiveTest="Hopkins Verbal Learning Test Total", cognitiveDomain="Verbal Memory", scoreType="Z-score"),
           data.table(monthsPostTx=13.1, n=28, mean= 0.15, sd=1.22, cognitiveTest="Trail Making Part B", cognitiveDomain="Exec Fxn", scoreType="Z-score"),
           data.table(monthsPostTx=13.1, n=28, mean= 0.30, sd=1.15, cognitiveTest="MAE Controlled Oral Word Association", cognitiveDomain="Verbal Ability/Language", scoreType="Z-score"),
           data.table(monthsPostTx=13.1, n=28, mean= 0.56, sd=1.29, cognitiveTest="Trail Making Part A", cognitiveDomain="Attn/Wkg Mem/Concentration", scoreType="Z-score"),
           data.table(monthsPostTx=13.1, n=28, mean=13.25, sd=2.03, cognitiveTest="WAIS-R Digit Symbol", cognitiveDomain="Information Proc Speed", scoreType="Scaled score"),
           data.table(monthsPostTx=13.1, n=28, mean=10.04, sd=2.67, cognitiveTest="WAIS-R Digit Span", cognitiveDomain="Attn/Wkg Mem/Concentration", scoreType="Scaled score"))
D <- D[,
       `:=` (author = "Wefel 2010",
             treatmentGroup = "Chemotherapy with or without paclitaxel")]
D4c <- D
print(xtable(D4c), type="html")
```


### Dumas

Reference: [Dumas 2013, *et al*](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3852152/).
*Brain Imaging Behav.* 2013 Dec; 7(4): 10.1007/s11682-013-9244-1.

Data is in the [Table 3](http://www.ncbi.nlm.nih.gov/pmc/articles/PMC3852152/table/T3/).

```{r, results='asis'}
D <- rbind(data.table(monthsPostTx= 0, cognitiveTest="0-back sensitivity ", mean=2.27, sd=0.9),
           data.table(monthsPostTx= 0, cognitiveTest="1-back sensitivity ", mean=1.70, sd=1.2),
           data.table(monthsPostTx= 0, cognitiveTest="2-back sensitivity ", mean=1.89, sd=0.8),
           data.table(monthsPostTx= 0, cognitiveTest="3-back sensitivity ", mean=1.32, sd=0.9),
           data.table(monthsPostTx=12, cognitiveTest="0-back sensitivity ", mean=2.40, sd=0.8),
           data.table(monthsPostTx=12, cognitiveTest="1-back sensitivity ", mean=2.29, sd=1.0),
           data.table(monthsPostTx=12, cognitiveTest="2-back sensitivity ", mean=1.68, sd=0.7),
           data.table(monthsPostTx=12, cognitiveTest="3-back sensitivity ", mean=1.60, sd=0.8),
           data.table(monthsPostTx= 0, cognitiveTest="0-back bias ", mean=0.20, sd=0.3),
           data.table(monthsPostTx= 0, cognitiveTest="1-back bias ", mean=0.22, sd=0.5),
           data.table(monthsPostTx= 0, cognitiveTest="2-back bias ", mean=0.05, sd=0.4),
           data.table(monthsPostTx= 0, cognitiveTest="3-back bias ", mean=0.61, sd=0.3),
           data.table(monthsPostTx=12, cognitiveTest="0-back bias ", mean=0.26, sd=0.3),
           data.table(monthsPostTx=12, cognitiveTest="1-back bias ", mean=0.06, sd=0.2),
           data.table(monthsPostTx=12, cognitiveTest="2-back bias ", mean=0.03, sd=.03),
           data.table(monthsPostTx=12, cognitiveTest="3-back bias ", mean=0.32, sd=0.2))
D <- D[,
       `:=` (author = "Dumas",
             treatmentGroup = "Chemotherapy +",
             cognitiveDomain = "Attn/Wkg Mem/Concentration",
             scoreType = "",
             n = 9)]
D4d <- D
print(xtable(D4d), type="html")
```


### Moore

Reference: [Moore 2014, *et al*](http://www.ncbi.nlm.nih.gov/pubmed/24647490).
*Support Care Cancer.* 2014 Aug;22(8):2127-31. doi: 10.1007/s00520-014-2197-0. Epub 2014 Mar 20.

Data was sent by the study author.

```{r, results='asis'}
D <- rbind(data.table(monthsPostTx= 0, cognitiveTest="WAIS-III Symbol Search"      , mean=29, sd= 6),
           data.table(monthsPostTx= 0, cognitiveTest="WAIS-III Digit Symbol Coding", mean=75, sd=14),
           data.table(monthsPostTx= 1, cognitiveTest="WAIS-III Symbol Search"      , mean=32, sd= 4),
           data.table(monthsPostTx= 1, cognitiveTest="WAIS-III Digit Symbol Coding", mean=74, sd= 8),
           data.table(monthsPostTx=12, cognitiveTest="WAIS-III Symbol Search"      , mean=33, sd= 4),
           data.table(monthsPostTx=12, cognitiveTest="WAIS-III Digit Symbol Coding", mean=74, sd=14))
D <- D[,
       `:=` (author = "Moore",
             treatmentGroup = "Chemotherapy",
             cognitiveDomain = "Info Proc Speed",
             scoreType = "",
             n = 7)]
D4e <- D
print(xtable(D4e), type="html")
```
