## Combine data from studies

Load data from

1. Ono
1. Ahles
1. Tager

```{r}
f <- sprintf("%s/%s", pathOut, "Ono.RData")
load(f, verbose=TRUE)
metadata$colNames
D1 <- D
colNames1 <- metadataD$colNames
f <- sprintf("%s/%s", pathOut, "Ahles.RData")
load(f, verbose=TRUE)
metadata$colNames
D2 <- D
f <- sprintf("%s/%s", pathOut, "Tager.RData")
load(f, verbose=TRUE)
metadata$colNames
D3 <- T
```

Structure of the data should be

* `author`
* `monthsPostTx`
* `treatmentGroup`
* `cognitiveDomainOriginal` (remove this column since we won't use it)
* `cognitiveDomain`
* `cognitiveTest`
* `scoreType`
* `n`
* `mean`
* `sd`

Restructure Ono.

```{r}
colOrder <- c("author",
              "monthsPostTx",
              "treatmentGroup",
              "cognitiveDomain",
              "cognitiveTest",
              "scoreType",
              "n",
              "mean",
              "sd")
setnames(D1,
         c("CogTest", "CognitiveDomainPrimary", "CognitiveDomainForMetaAnalysis", "ScoreTyp", "N"),
         c("cognitiveTest", "cognitiveDomainOriginal", "cognitiveDomain", "scoreType", "n"))
D1 <- D1[author == "Wefel", author := "Wefel 2004"]
D1 <- D1[scoreType == "z score", scoreType := "Z-score"]
D1 <- D1[scoreType == "Scaled scores", scoreType := "Scaled score"]
D1[,
   `:=` (cognitiveDomainOriginal = NULL)]
setcolorder(D1, c(colOrder, "age"))
```

Fix a data errors in Collins.
Remove a duplicate row.

```{r}
n0 <- nrow(D1)
D1 <- D1[!(author == "Collins" & monthsPostTx == 0 &
             cognitiveTest %in% c("Letter-number sequencing: WAIS-III", "Symbol search: WAIS-III"))]
message(sprintf("Removed %d rows", n0 - nrow(D1)))
```

Restructure Ahles.

```{r}
D2 <- D2[, author := "Ahles"]
setnames(D2,
         c("CognitiveDomainForMetaAnalysis", "txgrp", "Label", "N", "Mean", "StdDev"),
         c("cognitiveDomain", "treatmentGroup", "cognitiveTest", "n", "mean", "sd"))
D2[,
   `:=` (Variable = NULL,
         ptime = NULL,
         NObs = NULL,
         Median = NULL,
         scoreType = "Z-score")]
setcolorder(D2, colOrder)
```

Restructure Tager.

```{r}
D3 <- D3[, author := "Tager"]
setnames(D3,
         c("Label", "CognitiveDomainForMetaAnalysis", "N", "meanZ", "sdZ"),
         c("cognitiveTest", "cognitiveDomain", "n", "mean", "sd"))
D3[,
   `:=` (Variable = NULL,
         session = NULL,
         treatmentGroup = "Chemo",
         scoreType = "Z-score")]
setcolorder(D3, colOrder)
```

`rbindlist` the data.

```{r}
D <- rbindlist(list(D1, D2, D3, D4a, D4b, D4c, D4d), use.names=TRUE, fill=TRUE)
```

Fill in `age` for these studies.

```{r}
unique(D[is.na(age), author])
D <- D[author == "Ahles"     , age := 51.7]
D <- D[author == "Tager"     , age := 60.3]
D <- D[author == "Fan"       , age := 48]
D <- D[author == "McDonald"  , age := 52.9]
D <- D[author == "Wefel 2010", age := 48.8]
D <- D[author == "Dumas"     , age := 57.1]
```

Standardize age.

```{r}
age <- unique(D[, .(author, age)])
age <- age[, ageCentered := scale(age, center=TRUE, scale=FALSE)]
age[,
    .(meanRaw = mean(age),
      sdRaw = sd(age),
      meanCentered = mean(ageCentered),
      sdCentered = sd(ageCentered))]
age[order(age)]
D <- merge(D, age, by=c("author", "age"))
```

Identify tests where higher values are worse.

```{r, results='asis'}
D <- D[, 
       isHigherWorse := 
         (grepl("sec|time", cognitiveTest, ignore.case=TRUE) &
            !(grepl("4WSTM", cognitiveTest) | grepl("PASAT", cognitiveTest))) |
         grepl("pegboard", cognitiveTest, ignore.case=TRUE) |
         (grepl("stroop", cognitiveTest, ignore.case=TRUE) & !grepl("^stroop$", cognitiveTest, ignore.case=TRUE))|
         (grepl("trail", cognitiveTest, ignore.case=TRUE) & author != "Fan")]
tests <- unique(D[, .(isHigherWorse, cognitiveDomain, cognitiveTest)])
setorder(tests, isHigherWorse, cognitiveDomain, cognitiveTest)
print(xtable(tests[isHigherWorse == TRUE]), type="html")
print(xtable(tests[isHigherWorse == FALSE]), type="html")
```

Output to CSV for Kathleen to verify.
**No longer needed.**
See [issue #7](https://github.com/benjamin-chan/AEAfterBreastCaACT/issues/7).

```{r, eval=FALSE}
f <- "tests.csv"
write.csv(tests, f, row.names=FALSE)
```

Shorten domain labels.

```{r}
setnames(D, c("cognitiveDomain", "cognitiveTest"), c("domain", "test"))
D <- D[domain == "Attn/Wkg Mem/Concentration", domain := "Attn/Wkg Mem/Concen"]
D <- D[domain == "Verbal Memory", domain := "Verb Mem"]
D <- D[domain == "Visual Memory", domain := "Vis Mem"]
D <- D[domain == "Verbal Ability/Language", domain := "Verb Ability/Lang"]
# D <- D[domain == "Motor Speed", domain := ""]
D <- D[domain == "Information Proc Speed", domain := "Info Proc Speed"]
# D <- D[domain == "Exec Fxn", domain := ""]
# D <- D[domain == "Visuospatial", domain := ""]
D <- D[, domain := factor(domain)]
D[, .N, domain]
```

Trim leading and trailing whitespace.

```{r}
D <- D[, test := gsub("^[[:space:]]*", "", test)]
D <- D[, test := gsub("[[:space:]]*$", "", test)]
```

Standardize test labels.

```{r}
D <- D[, test := gsub(":", "", test)]
D <- D[, test := gsub("anival", "animal", test)]
D <- D[, test := gsub("Wechsler Memory Scale-3", "WMS-III", test)]
D <- D[, test := gsub("Trails A", "TMT A", test)]
D <- D[, test := gsub("Trail Making A", "TMT A", test)]
D <- D[, test := gsub("Trail Making Part A", "TMT A", test)]
D <- D[, test := gsub("TMT part A time", "TMT A", test)]
D <- D[, test := gsub("Trails B", "TMT B", test)]
D <- D[, test := gsub("Trail Making B", "TMT B", test)]
D <- D[, test := gsub("Trail Making Part B", "TMT B", test)]
D <- D[, test := gsub("TMT part B time", "TMT B", test)]
D <- D[, test := gsub(" in Seconds", ", sec", test)]
D <- D[, test := gsub("second", "sec", test)]
D <- D[, test := gsub(" - ", " ", test)]
D <- D[, test := gsub("WAIS-III -Arithmetic", "WAIS-III Arithmetic", test)]
D <- D[, test := gsub("WAIS-III Letter-number sequencing", "WAIS-III Letter-number", test)]
D <- D[, test := gsub("WAIS-III Number/Letter", "WAIS-III Letter-number", test)]
D <- D[, test := gsub("Spatial span WMS-III", "WMS-III Spatial span", test)]
D <- D[, test := gsub("Verbal fluency COWAT correct", "COWAT Verbal fluency correct", test)]
D <- D[, test := gsub("^Boston Naming Test number correct$", "Boston Naming Test", test)]
D <- D[, test := gsub("^Boston Naming$", "Boston Naming Test", test)]
D <- D[, test := gsub("Peg Board time", "Pegboard, sec", test)]
D <- D[, test := gsub("^Pegboard", "Grooved Pegboard", test)]
D <- D[, test := gsub("dominant hand", "Dom Hand", test)]
D <- D[, test := gsub("nondominant hand", "Nondom Hand", test)]
D <- D[, test := gsub("nonDom", "Nondom", test)]
D <- D[, test := gsub("Grooved Pegboard Test", "Grooved Pegboard", test)]
D <- D[, test := toTitleCase(test)]
D <- D[, test := gsub("4wstm", "4WSTM", test)]
D <- D[, test := gsub("TMT a", "TMT A", test)]
unique(D[, test])[order(unique(D[, test]))]
```

Create `slab` variable for study label.
Add additional information for Bender.

```{r}
D <- D[, slab := sprintf("%s: %s", author, test)]
D <- D[author == "Bender" & age == 40.11,
       slab := sprintf("%s (%s)", slab, "CT alone")]
D <- D[author == "Bender" & age == 44.13,
       slab := sprintf("%s (%s)", slab, "CT + tamoxifen")]
D <- D[, `:=` (treatmentGroup = NULL)]
```

Split the data into two versions

1. `DLong` Longitudinal (including all time points)
2. `DPrepost` Pre-post (pre-treatment and 12+ month post-treatment)

```{r}
D[, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
DLong <- D
DPre  <- D[monthsPostTx == 0]
DPre [, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
DPost <- D[12 <= monthsPostTx]
DPost[, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
key <- c("author", "age", "ageCentered", "domain", "test", "isHigherWorse", "scoreType", "slab")
setkeyv(DPre , key)
setkeyv(DPost, key)
DPrepost <- merge(DPre, DPost, suffixes=c("Pre", "Post"))
```

If the cognitive test where high values are worse,
then flip the signs so the pre-post difference will have the same direction as tests where high values are better.

```{r}
DPrepost <- DPrepost[isHigherWorse == TRUE,
                     `:=` (meanPre = -meanPre,
                           meanPost = -meanPost)]
message(sprintf("%d rows were flipped", nrow(DPrepost[isHigherWorse == TRUE])))
```

Calculate effect sizes.

```{r}
calcFixed <- function (D) {
  escalc("SMD", data=D,
         m1i=meanPost, sd1i=sdPost, n1i=nPost,
         m2i=meanPre,  sd2i=sdPre,  n2i=nPre)
}
l <- list(calcFixed(DPrepost[domain == "Attn/Wkg Mem/Concen"]),
          calcFixed(DPrepost[domain == "Verb Mem"]),
          calcFixed(DPrepost[domain == "Vis Mem"]),
          calcFixed(DPrepost[domain == "Verb Ability/Lang"]),
          calcFixed(DPrepost[domain == "Motor Speed"]),
          calcFixed(DPrepost[domain == "Info Proc Speed"]),
          calcFixed(DPrepost[domain == "Exec Fxn"]),
          calcFixed(DPrepost[domain == "Visuospatial"]))
DPrepost <- rbindlist(l)
```

Order the data.

```{r}
setorder(DPrepost, domain, author, test)
```

Remove studies with missing data.

```{r}
unique(DPrepost[is.na(yi), .(author, domain, test, yi)])
DPrepost <- DPrepost[!is.na(yi)]
```

Add `id` variable.
Will need this for the random effect.

```{r}
DPrepost <- DPrepost[, id := factor(1:nrow(DPrepost))]
```

Save working data tables to file.

```{r}
metadataPrepost <- makeMetadata(DPrepost)
metadataLong <- makeMetadata(DLong)
f <- sprintf("%s/%s", pathOut, "AllStudies.RData")
save(DPrepost, metadataPrepost, DLong, metadataLong, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
```
