# Combine data from studies

Load data from

1. Ono
1. Ahles
1. Tager

```{r}
f <- "Ono.RData"
load(f, verbose=TRUE)
metadata$colNames
D1 <- D
colNames1 <- metadataD$colNames
f <- "Ahles.RData"
load(f, verbose=TRUE)
metadata$colNames
D2 <- D
f <- "Tager.RData"
load(f, verbose=TRUE)
metadata$colNames
D3 <- T
```

Structure of the data should be

* `author`
* `monthsPostTx`
* `treatmentGroup`
* `cognitiveDomainOriginal` (remove this column since we won't use it)
* `cognitiveDomain`
* `cognitiveTest`
* `scoreType`
* `n`
* `mean`
* `sd`

Restructure Ono.

```{r}
colOrder <- c("author",
              "monthsPostTx",
              "treatmentGroup",
              "cognitiveDomain",
              "cognitiveTest",
              "scoreType",
              "n",
              "mean",
              "sd")
setnames(D1,
         c("CogTest", "CognitiveDomainPrimary", "CognitiveDomainForMetaAnalysis", "ScoreTyp", "N"),
         c("cognitiveTest", "cognitiveDomainOriginal", "cognitiveDomain", "scoreType", "n"))
D1 <- D1[author == "Wefel", author := "Wefel 2004"]
D1 <- D1[scoreType == "z score", scoreType := "Z-score"]
D1 <- D1[scoreType == "Scaled scores", scoreType := "Scaled score"]
D1[,
   `:=` (cognitiveDomainOriginal = NULL)]
setcolorder(D1, colOrder)
```

Fix a data errors in Collins.
Remove a duplicate row.

```{r}
n0 <- nrow(D1)
D1 <- D1[!(author == "Collins" & monthsPostTx == 0 &
             cognitiveTest %in% c("Letter-number sequencing: WAIS-III", "Symbol search: WAIS-III"))]
message(sprintf("Removed %d rows", n0 - nrow(D1)))
```

Restructure Ahles.

```{r}
D2 <- D2[, author := "Ahles"]
setnames(D2,
         c("CognitiveDomainForMetaAnalysis", "txgrp", "Label", "N", "Mean", "StdDev"),
         c("cognitiveDomain", "treatmentGroup", "cognitiveTest", "n", "mean", "sd"))
D2[,
   `:=` (Variable = NULL,
         ptime = NULL,
         NObs = NULL,
         Median = NULL,
         scoreType = "Z-score")]
setcolorder(D2, colOrder)
```

Restructure Tager.

```{r}
D3 <- D3[, author := "Tager"]
setnames(D3,
         c("Label", "CognitiveDomainForMetaAnalysis", "N", "meanZ", "sdZ"),
         c("cognitiveTest", "cognitiveDomain", "n", "mean", "sd"))
D3[,
   `:=` (Variable = NULL,
         session = NULL,
         treatmentGroup = "Chemo",
         scoreType = "Z-score")]
setcolorder(D3, colOrder)
```

`rbindlist` the data.

```{r}
D <- rbindlist(list(D1, D2, D3))
```

Identify timed tests.

```{r}
D <- D[, isTimed := grepl("sec|time", cognitiveTest, ignore.case=TRUE)]
```

Output to CSV for Kathleen to verify.

```{r}
tests <- unique(D[, .(isTimed, cognitiveDomain, cognitiveTest)])
setorder(tests, isTimed, cognitiveDomain, cognitiveTest)
f <- "tests.csv"
write.csv(tests, f, row.names=FALSE)
```

Save working data tables to file.

```{r}
metadata <- makeMetadata(D)
f <- "AllStudies.RData"
save(D, metadata, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
```
