## Combine data from studies

Load data from

1. Ono
1. Ahles
1. Tager
1. Schagen

```{r}
f <- sprintf("%s/%s", pathOut, "Ono.RData")
load(f, verbose=TRUE)
metadata$colNames
D1 <- D
colNames1 <- metadataD$colNames
f <- sprintf("%s/%s", pathOut, "Ahles.RData")
load(f, verbose=TRUE)
metadata$colNames
D2 <- D
f <- sprintf("%s/%s", pathOut, "Tager.RData")
load(f, verbose=TRUE)
metadata$colNames
D3 <- T
f <- sprintf("%s/%s", pathOut, "Schagen.RData")
load(f, verbose=TRUE)
metadata$colNames
D5 <- D
f <- sprintf("%s/%s", pathOut, "Bender2015.RData")
load(f, verbose=TRUE)
metadata$colNames
D6 <- D
```

Structure of the data should be

* `author`
* `monthsPostTx`
* `treatmentGroup`
* `cognitiveDomainOriginal` (remove this column since we won't use it)
* `cognitiveDomain`
* `cognitiveTest`
* `scoreType`
* `n`
* `mean`
* `sd`

Restructure Ono.

```{r}
colOrder <- c("author",
              "monthsPostTx",
              "treatmentGroup",
              "cognitiveDomain",
              "cognitiveTest",
              "scoreType",
              "n",
              "mean",
              "sd")
setnames(D1,
         c("CogTest", "CognitiveDomainPrimary", "CognitiveDomainForMetaAnalysis", "ScoreTyp", "N"),
         c("cognitiveTest", "cognitiveDomainOriginal", "cognitiveDomain", "scoreType", "n"))
D1 <- D1[author == "Wefel", author := "Wefel 2004"]
D1 <- D1[scoreType == "z score", scoreType := "Z-score"]
D1 <- D1[scoreType == "Scaled scores", scoreType := "Scaled score"]
D1[,
   `:=` (cognitiveDomainOriginal = NULL)]
setcolorder(D1, c(colOrder, "age"))
```

Fix a data errors in Collins.
Remove a duplicate row.

```{r}
n0 <- nrow(D1)
D1 <- D1[!(author == "Collins" & monthsPostTx == 0 &
             cognitiveTest %in% c("Letter-number sequencing: WAIS-III", "Symbol search: WAIS-III"))]
message(sprintf("Removed %d rows", n0 - nrow(D1)))
```

Restructure Ahles.

```{r}
D2 <- D2[, author := "Ahles"]
setnames(D2,
         c("CognitiveDomainForMetaAnalysis", "txgrp", "Label", "N", "Mean", "StdDev"),
         c("cognitiveDomain", "treatmentGroup", "cognitiveTest", "n", "mean", "sd"))
D2[,
   `:=` (Variable = NULL,
         ptime = NULL,
         NObs = NULL,
         Median = NULL,
         scoreType = "Z-score")]
setcolorder(D2, colOrder)
```

Restructure Tager.

```{r}
D3 <- D3[, author := "Tager"]
setnames(D3,
         c("Label", "CognitiveDomainForMetaAnalysis", "N", "meanZ", "sdZ"),
         c("cognitiveTest", "cognitiveDomain", "n", "mean", "sd"))
D3[,
   `:=` (Variable = NULL,
         session = NULL,
         treatmentGroup = "Chemo",
         scoreType = "Z-score")]
setcolorder(D3, colOrder)
```

`rbindlist` the data.

```{r}
D <- rbindlist(list(D1, D2, D3, D4a, D4b, D4c, D4d, D4e, D5, D6),
               use.names=TRUE,
               fill=TRUE)
```

Fill in `age` for these studies.

```{r}
unique(D[is.na(age), author])
D <- D[author == "Ahles"     , age := 51.7]
D <- D[author == "Tager"     , age := 60.3]
D <- D[author == "Fan"       , age := 48]
D <- D[author == "McDonald"  , age := 52.9]
D <- D[author == "Wefel 2010", age := 48.8]
D <- D[author == "Dumas"     , age := 57.1]
D <- D[author == "Moore"     , age := 53]
D <- D[author == "Schagen"   , age := 45.5]
```

Standardize age.

```{r}
age <- unique(D[, .(author, age)])
age <- age[, ageCentered := scale(age, center=TRUE, scale=FALSE)]
age[,
    .(meanRaw = mean(age),
      sdRaw = sd(age),
      meanCentered = mean(ageCentered),
      sdCentered = sd(ageCentered))]
age[order(age)]
D <- merge(D, age, by=c("author", "age"))
```

Fill in `education`, mean education, for these studies.

```{r}
unique(D[is.na(age), author])
D <- D[author == "Bender"    , education := 14.11]
D <- D[author == "Collins"   , education := 14.6]
D <- D[author == "Jenkins"   , education := 12.02]
D <- D[author == "Wefel 2004", education := 14]
D <- D[author == "Ahles"     , education := 15.7]
D <- D[author == "Tager"     , education := 16.6]
D <- D[author == "Fan"       , education := NA]
D <- D[author == "McDonald"  , education := 15.2]
D <- D[author == "Wefel 2010", education := 13.0]
D <- D[author == "Dumas"     , education := 15.3]
D <- D[author == "Moore"     , education := NA]
D <- D[author == "Schagen"   , education := NA]
```

Standardize education.

```{r}
education <- unique(D[, .(author, education)])
education <- education[, educationCentered := scale(education, center=TRUE, scale=FALSE)]
education[,
          .(meanRaw = mean(education),
            sdRaw = sd(education),
            meanCentered = mean(educationCentered),
            sdCentered = sd(educationCentered))]
education[order(education)]
D <- merge(D, education, by=c("author", "education"))
```

Use mean substitution for Moore and Schagen.
Moore and Schagen does not report education descriptive data for their cohorts.
Schagen reports IQ score.
Substitute the mean value of the other studies.

```{r}
D <- D[author == "Moore", educationCentered := 0]
D <- D[author == "Schagen", educationCentered := 0]
```

Identify tests where higher values are worse.

```{r, results='asis'}
D <- D[, 
       isHigherWorse := 
         (grepl("sec|time", cognitiveTest, ignore.case=TRUE) &
            !(grepl("4WSTM", cognitiveTest) | grepl("PASAT", cognitiveTest))) |
         grepl("pegboard", cognitiveTest, ignore.case=TRUE) |
         (grepl("stroop", cognitiveTest, ignore.case=TRUE) & !grepl("^stroop$", cognitiveTest, ignore.case=TRUE))|
         (grepl("trail", cognitiveTest, ignore.case=TRUE) & author != "Fan")]
tests <- unique(D[, .(isHigherWorse, cognitiveDomain, cognitiveTest)])
setorder(tests, isHigherWorse, cognitiveDomain, cognitiveTest)
print(xtable(tests[isHigherWorse == TRUE]), type="html")
print(xtable(tests[isHigherWorse == FALSE]), type="html")
```

Output to CSV for Kathleen to verify.
**No longer needed.**
See [issue #7](https://github.com/benjamin-chan/AEAfterBreastCaACT/issues/7).

```{r, eval=FALSE}
f <- "tests.csv"
write.csv(tests, f, row.names=FALSE)
```

Shorten domain labels.

```{r}
setnames(D, c("cognitiveDomain", "cognitiveTest"), c("domain", "test"))
D <- D[domain == "Attn/Wkg Mem/Concentration", domain := "Attn/Wkg Mem/Concen"]
D <- D[domain == "Verbal Memory", domain := "Verb Mem"]
D <- D[domain == "Visual Memory", domain := "Vis Mem"]
D <- D[domain == "Verbal Ability/Language", domain := "Verb Ability/Lang"]
# D <- D[domain == "Motor Speed", domain := ""]
D <- D[domain == "Information Proc Speed", domain := "Info Proc Speed"]
# D <- D[domain == "Exec Fxn", domain := ""]
# D <- D[domain == "Visuospatial", domain := ""]
D <- D[, domain := factor(domain)]
D[, .N, domain]
```

Trim leading and trailing whitespace.

```{r}
D <- D[, test := gsub("^[[:space:]]*", "", test)]
D <- D[, test := gsub("[[:space:]]*$", "", test)]
```

Standardize test labels.

```{r}
D <- D[, test := gsub(":", "", test)]
D <- D[, test := gsub("anival", "animal", test)]
D <- D[, test := gsub("Wechsler Memory Scale-3", "WMS-III", test)]
D <- D[, test := gsub("Trails A", "TMT A", test)]
D <- D[, test := gsub("Trail Making A", "TMT A", test)]
D <- D[, test := gsub("Trail Making Part A", "TMT A", test)]
D <- D[, test := gsub("TMT part A time", "TMT A", test)]
D <- D[, test := gsub("Trailmaking a", "TMT A", test)]
D <- D[, test := gsub("Trails B", "TMT B", test)]
D <- D[, test := gsub("Trail Making B", "TMT B", test)]
D <- D[, test := gsub("Trail Making Part B", "TMT B", test)]
D <- D[, test := gsub("TMT part B time", "TMT B", test)]
D <- D[, test := gsub("Trailmaking B", "TMT B", test)]
D <- D[, test := gsub(" in Seconds", ", sec", test)]
D <- D[, test := gsub("second", "sec", test)]
D <- D[, test := gsub(" - ", " ", test)]
D <- D[, test := gsub("WAIS-III -Arithmetic", "WAIS-III Arithmetic", test)]
D <- D[, test := gsub("WAIS-III Letter-number sequencing", "WAIS-III Letter-number", test)]
D <- D[, test := gsub("WAIS-III Number/Letter", "WAIS-III Letter-number", test)]
D <- D[, test := gsub("Spatial span WMS-III", "WMS-III Spatial span", test)]
D <- D[, test := gsub("Verbal fluency COWAT correct", "COWAT Verbal fluency correct", test)]
D <- D[, test := gsub("^Boston Naming Test number correct$", "Boston Naming Test", test)]
D <- D[, test := gsub("^Boston Naming$", "Boston Naming Test", test)]
D <- D[, test := gsub("Peg Board time", "Pegboard, sec", test)]
D <- D[, test := gsub("^Pegboard", "Grooved Pegboard", test)]
D <- D[, test := gsub("dominant hand", "Dom Hand", test)]
D <- D[, test := gsub("nondominant hand", "Nondom Hand", test)]
D <- D[, test := gsub("nonDom", "Nondom", test)]
D <- D[, test := gsub("Grooved Pegboard Test", "Grooved Pegboard", test)]
D <- D[, test := toTitleCase(test)]
D <- D[, test := gsub("4wstm", "4WSTM", test)]
D <- D[, test := gsub("TMT a", "TMT A", test)]
unique(D[, test])[order(unique(D[, test]))]
```

Create `slab` variable for study label.
Add additional information for Bender.

```{r}
D <- D[, slab := sprintf("%s: %s", author, test)]
D <- D[author == "Bender" & age == 40.11,
       slab := sprintf("%s (%s)", slab, "CT alone")]
D <- D[author == "Bender" & age == 44.13,
       slab := sprintf("%s (%s)", slab, "CT + tamoxifen")]
D <- D[, `:=` (treatmentGroup = NULL)]
```

Split the data into two versions

1. `DLong` Longitudinal (including all time points)
2. `DPrepost` Pre-post (pre-treatment and 12+ month post-treatment)

```{r}
D[, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
DLong <- D
DPre  <- D[monthsPostTx == 0]
DPre [, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
DPost <- D[12 <= monthsPostTx]
DPost[, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
key <- c("author", "age", "ageCentered", "education", "educationCentered",
         "domain", "test", "isHigherWorse", "scoreType", "slab")
setkeyv(DPre , key)
setkeyv(DPost, key)
DPrepost <- merge(DPre, DPost, suffixes=c("Pre", "Post"))
```

Add additional information for Schagen.
The 2006 paper's author is *Schagen*.
But the 2015 paper's author is actually *Stouten-Kemperman* (Schagen is the lat author).

```{r}
DPrepost <- DPrepost[author == "Schagen" & monthsPostTxPost == 12,
                     slab := sprintf("%s: %s", "Schagen", test)]
DPrepost <- DPrepost[author == "Schagen" & monthsPostTxPost == 138,
                     slab := sprintf("%s: %s", "Stouten-Kemperman", test)]
```

If the cognitive test where high values are worse,
then flip the signs so the pre-post difference will have the same direction as tests where high values are better.

```{r}
DPrepost <- DPrepost[isHigherWorse == TRUE,
                     `:=` (meanPre = -meanPre,
                           meanPost = -meanPost)]
message(sprintf("%d rows were flipped", nrow(DPrepost[isHigherWorse == TRUE])))
```

Calculate effect sizes.

```{r}
calcFixed <- function (D) {
  escalc("SMD", data=D,
         m1i=meanPost, sd1i=sdPost, n1i=nPost,
         m2i=meanPre,  sd2i=sdPre,  n2i=nPre)
}
l <- list(calcFixed(DPrepost[domain == "Attn/Wkg Mem/Concen"]),
          calcFixed(DPrepost[domain == "Verb Mem"]),
          calcFixed(DPrepost[domain == "Vis Mem"]),
          calcFixed(DPrepost[domain == "Verb Ability/Lang"]),
          calcFixed(DPrepost[domain == "Motor Speed"]),
          calcFixed(DPrepost[domain == "Info Proc Speed"]),
          calcFixed(DPrepost[domain == "Exec Fxn"]),
          calcFixed(DPrepost[domain == "Visuospatial"]))
DPrepost <- rbindlist(l)
```

Order the data.

```{r}
setorder(DPrepost, domain, author, test)
```

Remove studies with missing data.

```{r}
unique(DPrepost[is.na(yi), .(author, domain, test, yi)])
DPrepost <- DPrepost[!is.na(yi)]
```

Add `id` variable.
Will need this for the random effect.

```{r}
DPrepost <- DPrepost[, id := factor(1:nrow(DPrepost))]
```

Save working data tables to file.

```{r}
metadataPrepost <- makeMetadata(DPrepost)
metadataLong <- makeMetadata(DLong)
f <- sprintf("%s/%s", pathOut, "AllStudies.RData")
save(DPrepost, metadataPrepost, DLong, metadataLong, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
```
