## Combine data from studies

Load data from

1. Ono
1. Ahles
1. Tager

```{r}
f <- sprintf("%s/%s", pathOut, "Ono.RData")
load(f, verbose=TRUE)
metadata$colNames
D1 <- D
colNames1 <- metadataD$colNames
f <- sprintf("%s/%s", pathOut, "Ahles.RData")
load(f, verbose=TRUE)
metadata$colNames
D2 <- D
f <- sprintf("%s/%s", pathOut, "Tager.RData")
load(f, verbose=TRUE)
metadata$colNames
D3 <- T
```

Structure of the data should be

* `author`
* `monthsPostTx`
* `treatmentGroup`
* `cognitiveDomainOriginal` (remove this column since we won't use it)
* `cognitiveDomain`
* `cognitiveTest`
* `scoreType`
* `n`
* `mean`
* `sd`

Restructure Ono.

```{r}
colOrder <- c("author",
              "monthsPostTx",
              "treatmentGroup",
              "cognitiveDomain",
              "cognitiveTest",
              "scoreType",
              "n",
              "mean",
              "sd")
setnames(D1,
         c("CogTest", "CognitiveDomainPrimary", "CognitiveDomainForMetaAnalysis", "ScoreTyp", "N"),
         c("cognitiveTest", "cognitiveDomainOriginal", "cognitiveDomain", "scoreType", "n"))
D1 <- D1[author == "Wefel", author := "Wefel 2004"]
D1 <- D1[scoreType == "z score", scoreType := "Z-score"]
D1 <- D1[scoreType == "Scaled scores", scoreType := "Scaled score"]
D1[,
   `:=` (cognitiveDomainOriginal = NULL)]
setcolorder(D1, colOrder)
```

Fix a data errors in Collins.
Remove a duplicate row.

```{r}
n0 <- nrow(D1)
D1 <- D1[!(author == "Collins" & monthsPostTx == 0 &
             cognitiveTest %in% c("Letter-number sequencing: WAIS-III", "Symbol search: WAIS-III"))]
message(sprintf("Removed %d rows", n0 - nrow(D1)))
```

Restructure Ahles.

```{r}
D2 <- D2[, author := "Ahles"]
setnames(D2,
         c("CognitiveDomainForMetaAnalysis", "txgrp", "Label", "N", "Mean", "StdDev"),
         c("cognitiveDomain", "treatmentGroup", "cognitiveTest", "n", "mean", "sd"))
D2[,
   `:=` (Variable = NULL,
         ptime = NULL,
         NObs = NULL,
         Median = NULL,
         scoreType = "Z-score")]
setcolorder(D2, colOrder)
```

Restructure Tager.

```{r}
D3 <- D3[, author := "Tager"]
setnames(D3,
         c("Label", "CognitiveDomainForMetaAnalysis", "N", "meanZ", "sdZ"),
         c("cognitiveTest", "cognitiveDomain", "n", "mean", "sd"))
D3[,
   `:=` (Variable = NULL,
         session = NULL,
         treatmentGroup = "Chemo",
         scoreType = "Z-score")]
setcolorder(D3, colOrder)
```

`rbindlist` the data.

```{r}
D <- rbindlist(list(D1, D2, D3, D4a, D4b, D4c), use.names=TRUE)
```

Identify tests where higher values are worse.

```{r, results='asis'}
D <- D[, 
       isHigherWorse := 
         (grepl("sec|time", cognitiveTest, ignore.case=TRUE) &
            !(grepl("4WSTM", cognitiveTest) | grepl("PASAT", cognitiveTest))) |
         grepl("pegboard", cognitiveTest, ignore.case=TRUE) |
         (grepl("stroop", cognitiveTest, ignore.case=TRUE) & !grepl("^stroop$", cognitiveTest, ignore.case=TRUE))|
         (grepl("trail", cognitiveTest, ignore.case=TRUE) & author != "Fan")]
tests <- unique(D[, .(isHigherWorse, cognitiveDomain, cognitiveTest)])
setorder(tests, isHigherWorse, cognitiveDomain, cognitiveTest)
print(xtable(tests[isHigherWorse == TRUE]), type="html")
print(xtable(tests[isHigherWorse == FALSE]), type="html")
```

Output to CSV for Kathleen to verify.
**No longer needed.**
See [issue #7](https://github.com/benjamin-chan/AEAfterBreastCaACT/issues/7).

```{r, eval=FALSE}
f <- "tests.csv"
write.csv(tests, f, row.names=FALSE)
```

Merge pre-treatment measures to 12+ month post-treatment measures.

```{r}
D[, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
DPre  <- D[monthsPostTx == 0]
DPre [, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
DPost <- D[12 <= monthsPostTx]
DPost[, .N, .(author, monthsPostTx)][order(author, monthsPostTx)]
key <- c("author", "cognitiveDomain", "cognitiveTest", "isHigherWorse", "scoreType")
setkeyv(DPre , key)
setkeyv(DPost, key)
D <- merge(DPre, DPost, suffixes=c("Pre", "Post"))
```

If the cognitive test where high values are worse,
then flip the signs so the pre-post difference will have the same direction as tests where high values are better.

```{r}
D <- D[isHigherWorse == TRUE,
       `:=` (meanPre = -meanPre,
             meanPost = -meanPost)]
message(sprintf("%d rows were flipped", nrow(D[isHigherWorse == TRUE])))
```

Calculate effect sizes.

```{r}
calcFixed <- function (D) {
  escalc("SMD", data=D,
         m1i=meanPost, sd1i=sdPost, n1i=nPost,
         m2i=meanPre,  sd2i=sdPre,  n2i=nPre)
}
l <- list(calcFixed(D[cognitiveDomain == "Attn/Wkg Mem/Concentration"]),
          calcFixed(D[cognitiveDomain == "Verbal Memory"]),
          calcFixed(D[cognitiveDomain == "Visual Memory"]),
          calcFixed(D[cognitiveDomain == "Verbal Ability/Language"]),
          calcFixed(D[cognitiveDomain == "Motor Speed"]),
          calcFixed(D[cognitiveDomain == "Information Proc Speed"]),
          calcFixed(D[cognitiveDomain == "Exec Fxn"]),
          calcFixed(D[cognitiveDomain == "Visuospatial"]))
D <- rbindlist(l)
```

Shorten domain labels.

```{r}
setnames(D, c("cognitiveDomain", "cognitiveTest"), c("domain", "test"))
D <- D[domain == "Attn/Wkg Mem/Concentration", domain := "Attn/Wkg Mem/Concen"]
D <- D[domain == "Verbal Memory", domain := "Verb Mem"]
D <- D[domain == "Visual Memory", domain := "Vis Mem"]
D <- D[domain == "Verbal Ability/Language", domain := "Verb Ability/Lang"]
# D <- D[domain == "Motor Speed", domain := ""]
D <- D[domain == "Information Proc Speed", domain := "Info Proc Speed"]
# D <- D[domain == "Exec Fxn", domain := ""]
# D <- D[domain == "Visuospatial", domain := ""]
D <- D[, domain := factor(domain)]
D[, .N, domain]
```

Save working data tables to file.

```{r}
metadata <- makeMetadata(D)
f <- sprintf("%s/%s", pathOut, "AllStudies.RData")
save(D, metadata, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
```
