---
title: Cognitive Impairment
author: "[Benjamin Chan](http://careers.stackoverflow.com/benjaminchan)"
date: "`r Sys.time()`"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
    toc: yes
---

`source` the R script, `make.R` to generate the project document.

```
> source("make.R")
```

This document was generated on **`r Sys.time()`**.


# Project repository

*Live* version is stored here. *Static* version is this document.

* [Main](https://github.com/benjamin-chan/AEAfterBreastCaACT)
    * [Wiki](https://github.com/benjamin-chan/AEAfterBreastCaACT/wiki)
    * [Issues](https://github.com/benjamin-chan/AEAfterBreastCaACT/issues)
* Cognitive Impairment adverse event
    * [Wiki](https://github.com/benjamin-chan/AEAfterBreastCaACT/wiki/Cognitive-impairment)
    * [Meta-analysis](https://github.com/benjamin-chan/AEAfterBreastCaACT/tree/master/CognitiveImpairment#pooled-domain-effects)
    * [Forest plot](https://github.com/benjamin-chan/AEAfterBreastCaACT/blob/master/CognitiveImpairment/Output/forest.png)
    * [Funnel plot](https://github.com/benjamin-chan/AEAfterBreastCaACT/tree/master/CognitiveImpairment#plot-to-assess-publication-bias)


This document is for the **Cognitive Impairment** topic.

For other topics, see links from the project [repository](https://github.com/benjamin-chan/AEAfterBreastCaACT).


# Scripts

Sequence of scripts:

```{r, echo=FALSE}
scripts <- c("prologue.Rmd",
             "tidyData.Rmd",
             "runMetaAnalysis.Rmd",
             "epilogue.Rmd")
```

`r paste(scripts, collapse=" %>% ")`

```{r, echo=FALSE, fig.width=2, message=FALSE, warning=FALSE}
library(devtools)
source_gist("https://gist.github.com/benjamin-chan/f7dc918e2607b412ccf5", quiet=TRUE)
flow(scripts)
```

```{r, eval=TRUE, child=scripts}
```
