---
title: Risks of Long-term Cognitive Impairment in Breast Cancer Patients Treated with Adjuvant Chemotherapy
author: "[Benjamin Chan](http://careers.stackoverflow.com/benjaminchan)"
date: "`r Sys.time()`"
output: 
  html_document: 
    keep_md: yes
    number_sections: yes
    toc: yes
---

`source` the R script, `make.R` to generate the project document.

```
> source("make.R")
```

This document was generated on **`r Sys.time()`**.


# Project repository

*Live* version is stored here. *Static* version is this document.

* [Wiki](https://github.com/benjamin-chan/CogImpAfterBreastCaACT/wiki)
* [Meta-analysis](README.md#pooled-domain-effects)
* [Forest plot](Output/forest.png)
* [Funnel plot](Output/funnel.png)


This document is for the **Cognitive Impairment** topic.

For other topics, see links from the project [repository](https://github.com/benjamin-chan/AEAfterBreastCaACT).


# Scripts

Sequence of scripts:

```{r, echo=FALSE}
scripts <- c("prologue.Rmd",
             "tidyData.Rmd",
             "runMetaAnalysisPrePost.Rmd",
             "epilogue.Rmd")
```

`r paste(scripts, collapse=" %>% ")`

```{r, echo=FALSE, fig.width=2, message=FALSE, warning=FALSE}
library(devtools)
source_gist("https://gist.github.com/benjamin-chan/f7dc918e2607b412ccf5",
            filename="flow.R",
            quiet=TRUE)
flow(scripts)
```

```{r, eval=TRUE, child=scripts}
```
