## Read Schagen

Read data from 
[Schagen, et al.](http://www.ncbi.nlm.nih.gov/pubmed/17148777)
"Change in Cognitive Function After Chemotherapy: a Prospective Study in Breast Cancer Patients"
*JNCI*,
Vol. 98, No. 23, December 6, 2006.
and
[Stouten-Kemperman](http://www.ncbi.nlm.nih.gov/pubmed/24858488)
"Neurotoxicity in breast cancer survivors ???10 years post-treatment is dependent on treatment type."
*Brain Imaging and Behavior*
(2015) 9:275-284.

> From: Ayse Tezcan [mailto:aztezcan@ucdavis.edu]   
> Sent: Monday, May 16, 2016 8:59 AM  
> To: Joy Melnikow  
> Cc: Ganz, Patricia, M.D.; Meghan Soulsby; Benjamin Chan; Van Dyk, Kathleen  
> Subject: Re: Request to include your data in our meta-analysis of cognitive
> impairment  associated with breast cancer chemotherapy
> 
> This is great news!
> 
> Just to remind what the studies were:
> 
> * "Change in Cognitive Function After Chemotherapy: a Prospective Study in Breast Cancer Patients"" [JNCI, Vol. 98, No. 23, December 6, 2006](http://www.ncbi.nlm.nih.gov/pubmed/17148777)
> * "Neurotoxicity in breast cancer survivors ???10 years post-treatment is dependent on treatment type."" [Brain Imaging and Behavior (2015) 9:275-284](http://www.ncbi.nlm.nih.gov/pubmed/24858488)
> 
> The study compared 4 groups: FEC (Con-CT), CTC (high dose), No-chemo (RT-
> only) and healthy controls.
> 
> The 2015 study was a follow-up study to the 2006 study. For 2006 study, the
> follow-up assessment was 12 months after baseline, and for 2015 study, it
> was ???10 years.
> 
> 2015 study included 61.5% of the original FEC participants, 82% of CTC,
> 50.9% of RT-only and 66.7% of HCs.
> 
> **For our study, we only need the data from the FEC (Con-CT) group**; however,
> we can discuss the effect of high dose chemotherapy.

```{r}
f <- sprintf("%s/%s", pathIn, "Schagen Domains.xlsx")
echoFile(f)
varname <- c("cognitiveDomain", "cognitiveTest", "comment", "monthsPostTx")
D1 <- data.table(read.xlsx(f, sheet="2006"))
setnames(D1, names(D1), c(varname, "fec", "ctc", "noct", "control"))
D2 <- data.table(read.xlsx(f, sheet="2015"))
setnames(D2, names(D2), c(varname, "hict", "conct", "rtonly", "hc"))
```

From the 2006 data, remove the CTC, no-CT, and control columns.

```{r}
D1 <- D1[,
         `:=` (ctc = NULL,
               noct = NULL,
               control = NULL)]
```

From the 2015 data, remove the HI-CT, RT, and HC columns.

```{r}
D2 <- D2[,
         `:=` (hict = NULL,
               rtonly = NULL,
               hc = NULL)]
```

Add sample sizes.

```{r}
D1 <- D1[, n := 39]
D2 <- D2[, n := 24]
```

Split up the mean and SD values into separate columns.

```{r}
D1 <- D1[, 
         `:=` (mean = as.numeric(tstrsplit(fec, "\\(")[[1]]),
               sd = as.numeric(gsub(")", "", tstrsplit(fec, "\\(")[[2]])))]
D1 <- D1[, fec := NULL]
D2 <- D2[, 
         `:=` (mean = as.numeric(tstrsplit(conct, "\\(")[[1]]),
               sd = as.numeric(gsub(")", "", tstrsplit(conct, "\\(")[[2]])))]
D2 <- D2[, conct := NULL]
```

Clean up cognitive test labels.

```{r}
D1[, .N, cognitiveTest]
D1 <- D1[, cognitiveTest := gsub("\\s+[abc]\\s*$", "", cognitiveTest)]
D1[, .N, cognitiveTest]
D2 <- D2[, cognitiveTest := gsub("^\\s*", "", cognitiveTest)]
```

Remove the `Eriksen`, `AFM`, and `Memory update` tests from 2006 data.
Kathleen suggests

> This is not a standard clinical NP test - we may want to take out (Eriksen)

and

> This task seems to be an experimental measure - not sure if it should be included (AFM)

and

> I don't know what this test is (Memory update)

```{r}
D1 <- D1[grep("(Eriksen)|(AFM)|(Memory update)", cognitiveTest, invert=TRUE)]
```

Rename CVLT tests.

```{r}
D2 <- D2[cognitiveTest == "Verbal memory immediate recall", cognitiveTest := "CVLT recall"]
D2 <- D2[cognitiveTest == "Verbal memory delayed recall correct", cognitiveTest := "CVLT delayed recall"]
D2 <- D2[cognitiveTest == "Verbal memory cued recognition hits", cognitiveTest := "CVLT recognition"]
```

Identify tests used in both 2006 and 2015 publications.

```{r}
t1 <- unique(D1[, cognitiveTest])
t2 <- unique(D2[, cognitiveTest])
intersect(t1, t2)
```

Row bind the 2006 data to the 2015 data.

```{r}
D <- rbind(D1, D2)
```

Rename domain values.

```{r}
D[cognitiveDomain == "Attention", cognitiveDomain := "Attn/Wkg Mem/Concentration"]
# D[cognitiveDomain == "", cognitiveDomain := "Verbal Memory"]
# D[cognitiveDomain == "", cognitiveDomain := "Visual Memory"]
D[cognitiveDomain == "Language", cognitiveDomain := "Verbal Ability/Language"]
# D[cognitiveDomain == "", cognitiveDomain := "Motor Speed"]
D[cognitiveDomain == "Information Processing Speed", cognitiveDomain := "Information Proc Speed"]
D[grep("Executive Func", cognitiveDomain), cognitiveDomain := "Exec Fxn"]
# D[cognitiveDomain == "", cognitiveDomain := "Visuospatial"]
```

Add global variable values.

```{r}
D <- D[,
       `:=` (author = "Schagen",
             treatmentGroup = "FEC/CON-CT",
             scoreType = "Raw")]
```

Save working data tables to file.

```{r}
metadata <- makeMetadata(D)
f <- sprintf("%s/%s", pathOut, "Schagen.RData")
save(D, metadata, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
```
