## Read Bender 2015

Read data from 
[Bender, et al.](http://www.ncbi.nlm.nih.gov/pubmed/25906766)
"Patterns of change in cognitive function with anastrozole therapy."
*Cancer.* 2015 Aug 1;121(15):2627-36. doi: 10.1002/cncr.29393. Epub 2015 Apr 23.

Data provided by

> From: Sereika, Susan M [mailto:ssereika@pitt.edu]   
> Sent: Monday, May 23, 2016 6:40 AM  
> To: Benjamin Chan; Joy Melnikow; Ayse Zubeyde Tezcan  
> Cc: Bender, Catherine M  
> Subject: Summary Statistics Individual NP Tests for the Anastrozole Only Group from Bender et al., 2015  
> 
> Hello,
> 
> Attached is an SAS dataset containing the summary statistics (mean, STD, and
> n) for the 9 individual NP test values that were used in calculating the three
> reported composites (executive function, concentration, and visual working
> memory) at pretreatment (baseline) and at 6, 12, and 18 months post baseline
> for breast cancer survivors receiving anastrozole only from Bender et al.,
> 2015.


```{r}
f <- sprintf("%s/%s", pathIn, "bendersummarystats.sas7bdat")
echoFile(f)
D <- read_sas(f)
D <- data.table(D)
D <- D[, author := "Bender 2015"]
```

Melt the data.

```{r}
meltStat <- function (D, re, value.name, id.vars) {
  varnames <- grep(re, names(D), value=TRUE)
  D <- melt(D[, c(id.vars, varnames), with=FALSE],
            id.vars=id.vars,
            variable.name="test",
            value.name=value.name)
  D <- D[, test := gsub(re, "", test)]
  D
}
id.vars <- c("stime", "group")
D1 <- meltStat(D, "^mean_", "mean", id.vars)
D2 <- meltStat(D, "^std_", "sd", id.vars)
D3 <- meltStat(D, "^n_", "n", id.vars)
keyvar <- c(id.vars, "test")
D <- merge(D1, merge(D2, D3, by=keyvar, all=TRUE), by=keyvar, all=TRUE)
```

Create `monthsPostTx`.

```{r}
D <- D[stime == 0, monthsPostTx := 0]
D <- D[stime == 1, monthsPostTx := 6]
D <- D[stime == 2, monthsPostTx := 12]
D <- D[stime == 3, monthsPostTx := 18]
D <- D[, stime := NULL]
```

Add `cognitiveDomain` and `cognitiveTest`.

```{r}
domains <- data.frame(rbind(c("cftircl", "Complex Figure Test: Immediate Recall", "Vis Mem"),
                            c("cftdrcl", "Complex Figure Test: Delayed Recall", "Vis Mem"),
                            c("CFB005A1", "Digit Vigilance Test - Page 1 - Time (seconds)", "Attn/Wkg Mem/Concen"),
                            c("CFB005B1", "Digit Vigilance Test - Page 1 - Errors", "Attn/Wkg Mem/Concen"),
                            c("SWMTotalerrors", "SWM Total errors", "Attn/Wkg Mem/Concen"),
                            c("SWMStrategy", "SWM Strategy", "Attn/Wkg Mem/Concen"),
                            c("SOCMeaninitthinktime5moves", "SOC Mean initial thinking time (5 moves)", "Exec Fxn"),
                            c("SOCMeansubseqthinktime5mo", "SOC Mean subsequent thinking time (5 moves)", "Exec Fxn"),
                            c("SOCProblemssolvdinminmoves", "SOC Problems solved in minimum moves", "Exec Fxn")))
domains <- data.table(domains)
setnames(domains, names(domains), c("test", "cognitiveTest", "cognitiveDomain"))
D <- merge(D, domains, by="test")
D <- D[, test := NULL]
```