# Read Tager

Read data from 
[Tager, FA, et al.](http://link.springer.com/article/10.1007%2Fs10549-009-0606-8)
"The cognitive effects of chemotherapy in post-menopausal breast cancer patients: a controlled longitudinal study."
*Breast Cancer Res Treat.* 
  2010 Aug;123(1):25-34.

Data file was requested and received from the co-author, [Paula S. McKinley](pm491@cumc.columbia.edu), on November 20, 2015.

Read data file (SPSS format).

```{r}
f <- sprintf("%s/%s", pathIn, "Tager_DataForMetaAnalysis.sav")
echoFile(f)
D <- read_sav(f)
D <- data.table(D)
D <- D[,
       `:=` (session = factor(session,
                              levels = 1:4,
                              labels = c("Pre-surgery",
                                         "Post surgery before treatment",
                                         "Post treatment/6mths post surgery",
                                         "6 month follow-up")),
             chemoyn = factor(chemoyn,
                              levels= 0:1,
                              labels = c("No", "Yes")),
             CTregmen = factor(CTregmen,
                               levels = 1:3,
                               labels = c("AC",
                                          "ACT",
                                          "CMF")),
             tx = factor(tx,
                         levels = 0:11,
                         labels = c("None",
                                    "Chemo",
                                    "Radiation",
                                    "Tamoxifen",
                                    "Arimadex",
                                    "Chemo + Radiation",
                                    "Chemo + Tamoxifen",
                                    "Chemo + Arimadex",
                                    "Radiation + Tamoxifen",
                                    "Radiation + Arimadex",
                                    "Chemo + Radiation + Tamoxifen",
                                    "Chemo + Radiation + Arimadex")))]
```

Check data.

```{r}
D[, .N, .(chemoyn, CTregmen)]
D[, .N, .(chemoyn, chemowks)]
```

Keep *z*-score variables for these instruments.

* Finger Tapper - Dom Hand
* Finger Tapper - NonDom Hand
* Pegboard - Dom Hand
* Pegboard - Nondom Hand
* COWAT
* Boston Naming
* Trail Making A
* Trail Making B
* WAIS-III Digit Symbol
* WAIS-III Digit Span
* WAIS-III Arithmetic
* WAIS-III Number/Letter
* Rey Copy
* Buschke Total 
* Benton Visual Retention Correct

```{r}
measures <- c("tapdomz",
              "tapndomz",
              "pegdomz",
              "pegndomz",
              "cowz",
              "bntz",
              "trlaz",
              "trlbz",
              "dsymz",
              "dspaz",
              "aritz",
              "numz",
              "reyz",
              "bustotz",
              "bvrcoz")
```

Melt data.

```{r}
D <- melt(D,
          id.vars = c("subid", "session", "chemoyn", "chemowks", "CTregmen", "tx"),
          measure.vars = measures)
setnames(D, "variable", "Variable")
D <- D[Variable == "tapdomz", Label := "Finger Tapper - Dom Hand"]
D <- D[Variable == "tapndomz", Label := "Finger Tapper - NonDom Hand"]
D <- D[Variable == "pegdomz", Label := "Pegboard - Dom Hand"]
D <- D[Variable == "pegndomz", Label := "Pegboard - Nondom Hand"]
D <- D[Variable == "cowz", Label := "COWAT"]
D <- D[Variable == "bntz", Label := "Boston Naming"]
D <- D[Variable == "trlaz", Label := "Trail Making A"]
D <- D[Variable == "trlbz", Label := "Trail Making B"]
D <- D[Variable == "dsymz", Label := "WAIS-III Digit Symbol"]
D <- D[Variable == "dspaz", Label := "WAIS-III Digit Span"]
D <- D[Variable == "aritz", Label := "WAIS-III Arithmetic"]
D <- D[Variable == "numz", Label := "WAIS-III Number/Letter"]
D <- D[Variable == "reyz", Label := "Rey Copy"]
D <- D[Variable == "bustotz", Label := "Buschke Total "]
D <- D[Variable == "bvrcoz", Label := "Benton Visual Retention Correct"]
setkey(D, subid, session)
```

Exclude

* Non-chemotherapy patients
* Measurements before surgery

```{r}
D <- D[chemoyn != "No" &
         session != "Pre-surgery"]
D[, .N, .(chemoyn, session)]
```

Calculate means and standard deviations

```{r}
T <- D[,
       .(N = .N,
         meanZ = mean(value, na.rm=TRUE),
         sdZ = sd(value, na.rm=TRUE)),
       .(Variable,
         Label,
         session)]
setkey(T, Variable, Label, session)
```

Check against *Table 2*, column **CT Group** of [Tager, FA, et al.](http://link.springer.com/article/10.1007%2Fs10549-009-0606-8).

```{r}
T1 <- T[session == "Post surgery before treatment"]
T1 <- T1[, x := sprintf("%.2f (%.2f)", meanZ, sdZ)]
T1[, .(Variable, Label, N, x)]
```

Map `session` to *months after treatment*.
[Tager, FA, et al.](http://link.springer.com/article/10.1007%2Fs10549-009-0606-8)

* Baseline
* 1 month after treatment
* 6 months after treatment

As far as I can tell, values of `ptime` map to these, although seemingly imprecise.

```{r}
T <- T[session == "Post surgery before treatment", monthsPostTx := 0]
T <- T[session == "Post treatment/6mths post surgery", monthsPostTx := 6]
T <- T[session == "6 month follow-up", monthsPostTx := 12]
```

Merge Kathleen's <KVanDyk@mednet.ucla.edu> domain assignments.

```
From: Van Dyk, Kathleen [KVanDyk@mednet.ucla.edu]
Sent: Tuesday, November 03, 2015 5:08 PM
To: Ayse Tezcan
Cc: Benjamin Chan
Subject: RE: Cognitive impairment draft paper

Hi,
 
Attached is the Ono spreadsheet with a new column with my suggestions for
domains and domains for each Ahles test is in sheet 2.  I've highlighted tests
that we may want to exclude if we want to consistently keep one or two
measures per test.  Ben --- does it matter statistically if there is more than
one measure from the same test (for example delayed recall and delayed
recognition) in the same domain?  In almost every case we have total and delay
for memory tests but if we add in more measures (Trial 6, Supraspan,
Recognition) does this confound analyses because these are likely highly
correlated measures within the same test?  Would all of the studies need to
use the same measures in each test (i.e., every study uses Total and Delay)?
I might not be asking this clearly --- let me know what you think.
```

```{r}
f <- sprintf("%s/%s", pathIn, "Requested Chemo Data domains kvd 11.19.15 2.xlsx")
echoFile(f)
D0 <- read.xlsx(f, sheet=1, check.names=TRUE)
D0 <- data.table(D0)
D0 <- D0[First.Auth == "Tager" & !is.na(DOMAIN.FOR.META..kvd.),
         .(Label = Cog.Test,
           CognitiveDomainForMetaAnalysis = DOMAIN.FOR.META..kvd.)]
D0 <- D0[Label == "WAIS-IIIDigit Span",
         Label := "WAIS-III Digit Span"]
lookup <- D0
T <- merge(lookup, T, by="Label")
```

Save working data tables to file.

```{r}
metadata <- makeMetadata(T)
f <- "Tager.RData"
save(T, metadata, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
```
