## Reshape Ono

Reshape the Ono data set so it has a similar structure to the Ahles and Tager data.

```{r}
f <- sprintf("%s/%s", pathOut, "Ono.RData")
load(f, verbose=TRUE)
metadata$timeStamp
metadata$colNames
```

Melt data.

```{r}
idVars <- c("author",
            "comparisonGroup",
            "treatmentGroup",
            "timeDays",
            "CogTest",
            "CognitiveDomainPrimary",
            "CognitiveDomainForMetaAnalysis",
            "ScoreTyp",
            "ageGroup1")
DN <- melt(D, id.vars = idVars,
           measure.vars = c("nGroup1", "nGroup2"), value.name = "N",
           na.rm=TRUE)
DMean <- melt(D, id.vars = idVars,
              measure.vars = c("meanGroup1", "meanGroup2"), value.name = "mean",
              na.rm=TRUE)
DSD <- melt(D, id.vars = idVars,
            measure.vars = c("sdGroup1", "sdGroup2"), value.name = "sd",
            na.rm=TRUE)
```

Check studies.
**Do not show**

```{r, results='hide'}
D[, .N, .(author, comparisonGroup, treatmentGroup, timeDays, ageGroup1)]
```

Prepare measure data sets for merging.

```{r}
DN    <- DN   [variable == "nGroup1"   , group := "Group 1"]
DMean <- DMean[variable == "meanGroup1", group := "Group 1"]
DSD   <- DSD  [variable == "sdGroup1"  , group := "Group 1"]
DN    <- DN   [variable == "nGroup2"   , group := "Group 2"]
DMean <- DMean[variable == "meanGroup2", group := "Group 2"]
DSD   <- DSD  [variable == "sdGroup2"  , group := "Group 2"]
```

Merge the melted data.

```{r}
setkeyv(DN, c(idVars, "group"))
setkeyv(DMean, c(idVars, "group"))
setkeyv(DSD, c(idVars, "group"))
D <- merge(DN[, variable := NULL], DMean[, variable := NULL])
D <- merge(D, DSD[, variable := NULL])
```

Deduplicate pre-treatment data.

```{r}
D1 <- D[group == "Group 1"]
setkeyv(D1, idVars[!(idVars %in% c("comparisonGroup", "treatmentGroup", "timeDays"))])
D1 <- unique(D1)
D1 <- D1[, monthsPostTx := 0]
D1 <- D1[,
         `:=` (comparisonGroup = NULL,
               treatmentGroup = NULL,
               timeDays = NULL,
               group = NULL)]
```

Calculate `monthsPostRx` for post-treatment values.

```{r}
D2 <- D[group == "Group 2"]
D2 <- D2[, monthsPostTx := round(timeDays / 365.25 * 12)]
D2 <- D2[,
         `:=` (comparisonGroup = NULL,
               timeDays = NULL,
               group = NULL)]
```

`rbind` pre-treatment and post-treatment data.

```{r}
D <- rbind(D1, D2, fill=TRUE)
```

Check data structure

```{r}
unique(D[, .(author, monthsPostTx)])[order(author, monthsPostTx)]
```

Rename the age variable.

```{r}
setnames(D, "ageGroup1", "age")
```

Overwrite the data to file.

```{r}
metadata <- makeMetadata(D)
f <- sprintf("%s/%s", pathOut, "Ono.RData")
save(D, metadata, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
```
