# Meta-analysis

Load tidy data.

```{r}
f <- sprintf("%s/%s", pathOut, "AllStudies.RData")
load(f, verbose=TRUE)
metadata$timeStamp
metadata$colNames
```

Remove studies with missing data.

```{r}
D <- D[!is.na(yi)]
```

Label each data point.
Will need this for the multilevel random effects model specification.

```{r}
D <- D[, j := factor(sequence(D[, .N, .(author, cognitiveDomain)][, N]))]
```

## Pooled effects by domain

Each domain is modeled with a multilevel random effects model.

```{r, results='asis'}
domains <- unique(D[, cognitiveDomain])
n <- D[, .N, cognitiveDomain][, N]
models <- list()
summary <- data.frame()
for (i in 1:length(domains)) {
  models[[i]] <- rma.mv(yi, vi,
                        random = list(~ author | j, ~ 1 | author), struct="ID",
                        data=D[cognitiveDomain == domains[i]],
                     slab=sprintf("%s: %s", author, cognitiveTest))
  summaryi <- data.frame(models[[i]][c("k", "b", "se", "zval", "pval", "ci.lb", "ci.ub", "sigma2", "tau2", "rho", "QE", "QEp")])
  summary <- rbind(summary, summaryi)
}
rownames(summary) <- NULL
summary <- cbind(domain = domains, summary)
print(xtable(summary, digits=c(rep(0, 3), rep(2, 3), 4, rep(2, 2), rep(5, 3), 2, 5)), type="html")
```

Save working data tables to file.

```{r}
metadata <- makeMetadata(D)
f <- sprintf("%s/%s", pathOut, "metaAnalysisCognitiveImpairment.RData")
save(D, metadataD, domains, models, summary, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
f <- sprintf("%s/%s", pathOut, "metaAnalysisCognitiveImpairment-Data.csv")
write.csv(D, file=f, row.names=FALSE)
f <- sprintf("%s/%s", pathOut, "metaAnalysisCognitiveImpairment-summary.csv")
write.csv(summary, file=f, row.names=FALSE)
```


## Plots of effect sizes by domain

The `xlim` settings require fine-tuning.

```{r, echo=FALSE}
h <- sqrt(n) * 2
lower <- D$yi + qnorm(0.025) * sqrt(D$vi)
upper <- D$yi + qnorm(0.975) * sqrt(D$vi)
alim <- c(floor(min(lower, na.rm=TRUE)), ceiling(max(upper, na.rm=TRUE)))
xlim <- c(-12, 9)
at <- seq(floor(min(lower, na.rm=TRUE)), ceiling(max(upper, na.rm=TRUE)), 1)
```

```{r forest1, echo=FALSE, fig.width=10, fig.height=h[1]}
forest(models[[1]], main=domains[1],
       mlab="Pooled random effect", alim=alim, xlim=xlim, at=at)
```

```{r forest2, echo=FALSE, fig.width=10, fig.height=h[2]}
forest(models[[2]], main=domains[2],
       mlab="Pooled random effect", alim=alim, xlim=xlim, at=at)
```

```{r forest3, echo=FALSE, fig.width=10, fig.height=h[3]}
forest(models[[3]], main=domains[3],
       mlab="Pooled random effect", alim=alim, xlim=xlim, at=at)
```

```{r forest4, echo=FALSE, fig.width=10, fig.height=h[4]}
forest(models[[4]], main=domains[4],
       mlab="Pooled random effect", alim=alim, xlim=xlim, at=at)
```

```{r forest5, echo=FALSE, fig.width=10, fig.height=h[5]}
forest(models[[5]], main=domains[5],
       mlab="Pooled random effect", alim=alim, xlim=xlim, at=at)
```

```{r forest6, echo=FALSE, fig.width=10, fig.height=h[6]}
forest(models[[6]], main=domains[6],
       mlab="Pooled random effect", alim=alim, xlim=xlim, at=at)
```

```{r forest7, echo=FALSE, fig.width=10, fig.height=h[7]}
forest(models[[7]], main=domains[7],
       mlab="Pooled random effect", alim=alim, xlim=xlim, at=at)
```

```{r forest8, echo=FALSE, fig.width=10, fig.height=h[8]}
forest(models[[8]], main=domains[8],
       mlab="Pooled random effect", alim=alim, xlim=xlim, at=at)
```


## Plots to assess publication bias

See [*BMJ* 2011;342:d4002](http://www.bmj.com/content/343/bmj.d4002) for a guide to interpret funnel plots.

```{r funnel, echo=FALSE}
for (i in 1:length(domains)) {
  funnel(models[[i]], main=domains[i])
}
```
