# Meta-analysis, pre-post

Standardized mean differences (SMD) between pre-treatment and 12+ month post-treatment cognitive impairment measures is modeled with a multilevel mixed effects model.
Cognitive domain is modeled as a fixed effect, with one effect size for each of the 8 domains.
In our meta-analysis, we have multiple SMDs from each study
(one for each cognitive test reported).
Instead of modeling the random effect as a single parameter
(as we would if we only had one observed SMD per study),
we partition the random effect into variance components for observed SMD *i* and for study.
The two variance components allow for the computation of an intraclass correlation.
In addition, study-level mean age and years of education are included as covariates.

* Age is centered around a mean of `r sprintf("%.3g", attributes(D[, ageCentered])["scaled:center"])`.
* Education is centered around a mean of `r sprintf("%.3g", attributes(D[, educationCentered])["scaled:center"])`.

Therefore, the main effects from the models with these covariates are the estimates at the covariate means.

Mathematically, the model is represented as

<math xmlns="http://www.w3.org/1998/Math/MathML" display="block">
  <msub>
    <mi>y</mi>
    <mi>i</mi>
  </msub>
  <mo>=</mo>
  <munder>
    <mo>&#x2211;<!-- ??? --></mo>
    <mrow class="MJX-TeXAtom-ORD">
      <mi>j</mi>
      <mo>=</mo>
      <mn>1</mn>
    </mrow>
  </munder>
  <msub>
    <mi>&#x03B2;<!-- ?? --></mi>
    <mi>j</mi>
  </msub>
  <msub>
    <mi>x</mi>
    <mrow class="MJX-TeXAtom-ORD">
      <mi>i</mi>
      <mo>,</mo>
      <mtext>domain&#xA0;</mtext>
      <mi>j</mi>
    </mrow>
  </msub>
  <mo>+</mo>
  <msub>
    <mi>&#x03B3;<!-- ?? --></mi>
    <mtext>age</mtext>
  </msub>
  <msub>
    <mi>x</mi>
    <mrow class="MJX-TeXAtom-ORD">
      <mi>i</mi>
      <mo>,</mo>
      <mtext>age</mtext>
    </mrow>
  </msub>
  <mo>+</mo>
  <msub>
    <mi>&#x03B3;<!-- ?? --></mi>
    <mtext>education</mtext>
  </msub>
  <msub>
    <mi>x</mi>
    <mrow class="MJX-TeXAtom-ORD">
      <mi>i</mi>
      <mo>,</mo>
      <mtext>education</mtext>
    </mrow>
  </msub>
  <mo>+</mo>
  <msub>
    <mi>&#x03C3;<!-- ?? --></mi>
    <mi>i</mi>
  </msub>
  <mo>+</mo>
  <msub>
    <mi>&#x03C3;<!-- ?? --></mi>
    <mtext>study</mtext>
  </msub>
</math>

A second model to estimate a global SMD is

<math xmlns="http://www.w3.org/1998/Math/MathML" display="block">
  <msub>
    <mi>y</mi>
    <mi>i</mi>
  </msub>
  <mo>=</mo>
  <mi>&#x03B2;<!-- ?? --></mi>
  <mo>+</mo>
  <msub>
    <mi>&#x03B3;<!-- ?? --></mi>
    <mtext>age</mtext>
  </msub>
  <msub>
    <mi>x</mi>
    <mrow class="MJX-TeXAtom-ORD">
      <mi>i</mi>
      <mo>,</mo>
      <mtext>age</mtext>
    </mrow>
  </msub>
  <mo>+</mo>
  <msub>
    <mi>&#x03B3;<!-- ?? --></mi>
    <mtext>education</mtext>
  </msub>
  <msub>
    <mi>x</mi>
    <mrow class="MJX-TeXAtom-ORD">
      <mi>i</mi>
      <mo>,</mo>
      <mtext>education</mtext>
    </mrow>
  </msub>
  <mo>+</mo>
  <msub>
    <mi>&#x03C3;<!-- ?? --></mi>
    <mi>i</mi>
  </msub>
  <mo>+</mo>
  <msub>
    <mi>&#x03C3;<!-- ?? --></mi>
    <mtext>study</mtext>
  </msub>
</math>

Models were estimated using the `rma.mv()` function from the `metafor` package for R.

```{r}
citation("metafor")
```

An additional reference is

[Konstantopoulos, S. (2011)](http://onlinelibrary.wiley.com/doi/10.1002/jrsm.35/abstract), Fixed effects and variance components estimation in three-level meta-analysis. *Res. Synth. Method*, 2: 61-76. doi: 10.1002/jrsm.35

Load tidy data.

```{r}
f <- sprintf("%s/%s", pathOut, "AllStudies.RData")
load(f, verbose=TRUE)
metadataPrepost$timeStamp
metadataPrepost$colNames
D <- DPrepost
```

* `M1` models domain SMDs
* `M2` models the global SMD
* `M0` models domain SMDs without confounders

```{r}
randomEffect <- list(~ 1 | id, ~ 1 | author)
M1 <- rma.mv(yi ~ domain - 1 + ageCentered + educationCentered,
M0 <- rma.mv(yi ~ domain - 1,
             vi, data=D, random=randomEffect, slab=slab)
             vi, data=D, random=randomEffect, slab=slab)
M2 <- rma.mv(yi ~ ageCentered + educationCentered,
             vi, data=D, random=randomEffect)
```

```{r}
betasM0 <- data.frame(M0[c("b", "se", "zval", "pval", "ci.lb", "ci.ub")])
betasM1 <- data.frame(M1[c("b", "se", "zval", "pval", "ci.lb", "ci.ub")])
betasM2 <- data.frame(M2[c("b", "se", "zval", "pval", "ci.lb", "ci.ub")])
j <- grep("domain", rownames(M1$b))
summary <- rbind(data.frame(studies = D[, .(studies = uniqueN(author)), domain][, studies],
                            tests = D[, .N, domain][, N],
                            betasM1[j, ]),
                 data.frame(studies = D[, .(studies = uniqueN(author))][, studies],
                            tests = D[, .N],
                            betasM2[1, ]))
rownames(summary) <- gsub("domain", "", rownames(summary))
rownames(summary) <- gsub("intrcpt", "**GLOBAL**", rownames(summary))
```


## Pooled domain effects

```{r, echo=FALSE, results='asis'}
print(xtable(summary,
             caption="Pooled domain and global effect sizes at mean covariate values",
             digits=c(0, rep(0, 2), rep(3, 3), 4, rep(3, 2))),
      type="html",
      caption.placement="top")
```

The intraclass correlation within study is `r sprintf("%.3g", M1$sigma2[2] / sum(M1$sigma2))`.

```{r}
summary(M0)
summary(M1)
summary(M2)
```

Save working data tables to file.

```{r}
metadata <- makeMetadata(D)
f <- sprintf("%s/%s", pathOut, "metaAnalysisCognitiveImpairment.RData")
save(D, metadata, M0, M1, M2, summary, file=f)
message(sprintf("%s saved on: %s\nFile size: %s KB", 
                f,
                file.mtime(f),
                file.size(f) / 1e3))
f <- sprintf("%s/%s", pathOut, "metaAnalysisCognitiveImpairment-Data.csv")
write.csv(D, file=f, row.names=FALSE)
f <- sprintf("%s/%s", pathOut, "metaAnalysisCognitiveImpairment-summary.csv")
write.csv(summary, file=f, row.names=FALSE)
```


## Forest plot

```{r forest, echo=FALSE}
f <- sprintf("%s/%s", pathOut, "forest.png")
png(f, width=6, height=20, units="in", res=600)
lower <- D$yi + qnorm(0.025) * sqrt(D$vi)
upper <- D$yi + qnorm(0.975) * sqrt(D$vi)
alim <- c(floor(min(lower, na.rm=TRUE)), ceiling(max(upper, na.rm=TRUE)))
xlim <- c(-11, 10.5)
at <- seq(floor(min(lower, na.rm=TRUE)), ceiling(max(upper, na.rm=TRUE)), 2)
cex <- 1/2
n <- D[, .N, domain][order(-domain)][, N]
yoffset <- 3
ygap <- 3
rows <- c(1:n[1],
          1:n[2] + sum(n[1:(2 - 1)]) + ygap * (2 - 1),
          1:n[3] + sum(n[1:(3 - 1)]) + ygap * (3 - 1),
          1:n[4] + sum(n[1:(4 - 1)]) + ygap * (4 - 1),
          1:n[5] + sum(n[1:(5 - 1)]) + ygap * (5 - 1),
          1:n[6] + sum(n[1:(6 - 1)]) + ygap * (6 - 1),
          1:n[7] + sum(n[1:(7 - 1)]) + ygap * (7 - 1),
          1:n[8] + sum(n[1:(8 - 1)]) + ygap * (8 - 1)) + yoffset
rowHead <- c(n[8] + sum(n[1:(8 - 1)]) + ygap * (8 - 1),
             n[7] + sum(n[1:(7 - 1)]) + ygap * (7 - 1),
             n[6] + sum(n[1:(6 - 1)]) + ygap * (6 - 1),
             n[5] + sum(n[1:(5 - 1)]) + ygap * (5 - 1),
             n[4] + sum(n[1:(4 - 1)]) + ygap * (4 - 1),
             n[3] + sum(n[1:(3 - 1)]) + ygap * (3 - 1),
             n[2] + sum(n[1:(2 - 1)]) + ygap * (2 - 1),
             n[1]) + yoffset + 1
rowFoot <- c(sum(n[1:(8 - 1)]) + ygap * (8 - 1),
             sum(n[1:(7 - 1)]) + ygap * (7 - 1),
             sum(n[1:(6 - 1)]) + ygap * (6 - 1),
             sum(n[1:(5 - 1)]) + ygap * (5 - 1),
             sum(n[1:(4 - 1)]) + ygap * (4 - 1),
             sum(n[1:(3 - 1)]) + ygap * (3 - 1),
             sum(n[1:(2 - 1)]) + ygap * (2 - 1),
             0) + yoffset
forest(M1,
       order=order(D[, sprintf("%s %s %s", domain, author, test)], decreasing=TRUE),
       rows=rows,
       ylim=c(0, max(rows) + ygap + 1),
       addfit=FALSE,
       cex=cex,
       efac=0,
       alim=alim, xlim=xlim, at=at)
text(xlim[1], rowHead, levels(D[, domain]),
     pos=4, cex=cex, font=2)
addpoly(M1$b[j], diag(M1$vb)[j], M1$se[j], M1$ci.lb[j], M1$ci.ub[j],
        rows=rowFoot,
        mlab=rep("Pooled domain effect", length(M1$b)),
        cex=cex, font=2, col="blue", border="blue", efac=cex)
addpoly(M2$b[1], diag(M2$vb)[1], M2$se[1], M2$ci.lb[1], M2$ci.ub[1],
        rows=0,
        mlab="Pooled global effect",
        cex=cex, font=2, col="blue", border="blue", efac=cex)
text(-1, -2, "Impairment", adj=1, cex=cex)
text( 1, -2, "Improvement", adj=0, cex=cex)
dev.off()
```

Full resolution file is [here](Output/forest.png).


## Diagnostic plots

Check the profile likelihoods of the variance and correlation components.

```{r profile, echo=FALSE}
par(mfrow=c(2, 1))
profile(M1)
```

Funnel plot to check for publication bias.
See [*BMJ* 2011;342:d4002](http://www.bmj.com/content/343/bmj.d4002) for a guide to interpret funnel plots.

```{r funnel, echo=FALSE}
par(mfrow=c(1, 1))
f <- sprintf("%s/%s", pathOut, "funnel.png")
png(f, width=6, height=6, units="in", res=600)
funnel(M1)
dev.off()
funnel(M1)
```

Publication bias does not appear to be a great concern.
